* Identify four aspects of digital paywall design 
* Evaluate changes in paywall design on content demand and subscription behaviour
* Evaluate whether Amazon exploits changes in market power by changing prices


Market power of large online retailers 

* [He, Reimers & Shiller (2021)](https://benjaminshiller.com/pdfs/toy_paper.pdf)

Digital paywall design 

* [Aral and Dhillon (2021)](https://doi.org/10.1287/mnsc.2020.3650)

---
class: inverse, center, middle

# Market Power of the Giants

---
class: font150
# Motivation 

Large **online retailers** becoming **dominant players** in consumer markets 

Tradeoff: 

* Reputation for **consumer friendliness** & **lower search costs**, vs 
* Increased **market power**, **potential** to **increase prices** 

**Strategic Question**: How does Amazon adjust prices when its market power increases 

* Setting: Shut down of Toys R Us in the US due to bankruptcy

**Why this matters?**

* Anti-trust concerns (market power, abuse of dominance)
* How do smaller companies compete?
  * Not directly answered here

---
class: font140
# Data & Methodology

**Data**: 2016-18 US and Canada,approx 200,000 products on Amazon, 40,000 are toys

* Affected Products: Toys & Baby products
* Unaffected Products: home and kitchen, electronics, pet supplies, and beauty
* Sold by Amazon and third-party sellers on Amazon

**Methods**: Triple Difference 

* "Difference in the difference of differences"
* This is Differences in Differences with an additional layer of differencing
* Why?
  * Essentially authors worry about what the right control group is

---
# Data & Methodology

* Within US Diff in Diff (across product categories):

$$\ln(P_{it}) = \beta_1 Toy_i \times After_t + \gamma_i + \mu_t +\varepsilon_{it}$$

 .center[.font80[Are non-toys the right control group?]]

* US and Canada Diff in Diff (toys only):

$$\ln(P_{ict}) = \beta_1 After_t \times US_c + \phi_{it} + \psi_{ic} + \varepsilon_{ict}$$

 .center[.font80[Country Specific tastes, or country specific demand or supply shocks]]

* Triple Diff: 

$$\ln(P_{ict}) = \beta_1 US_c \times Toy_i \times After_t + \varphi_{it} + \omega_{ct} + \psi_{ic} + \varepsilon_{ict}$$

 .center[.font120[**Eliminates both concerns**]]

---
class: font160
# Main Result 

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/market_power_main.png"
knitr::include_graphics(url)
```

* **Prices rise** by 3.1% on Amazon 
* **Change** price **less frequently** (11.1%)
  * $\rightarrow$ indirect evidence of less promotions

---
class: font160
# Differential Effects

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/market_power_heterog.png"
knitr::include_graphics(url)
```

* Effects **concentrated** among **products sold more often**

---
class: font160
# Takeaways

* Big tech firms becoming **dominant players in consumer markets** 

* Evidence that when Amazon's **market power rises** (exogenously) that they **increase prices** 

* **Remark**: This is exactly what economic theory predicts
  * So its not "shocking" in any sense 
  * But is different from the typical things anti-trust regulators go after big tech for 
  * And might provide insight into the future as their dominant positions consolidate further

---
class: inverse, center, middle

# Digital Paywall Design

---
class: font140
# Motivation 

**Paywalls dominate the online content publishing landscape**

* Usually with a "freemium" design 
  * Maximizing revenue by regulating subscribers 
  * Think of a tradeoff between pure ad based revenue and subscription revenue

**Why not paywall everything?** (Some publishers do)

* High willingness to pay subscribers will subscribe, but
* Reduces exposure to new customers  
* Difficult for consumers to assess how content matches their preferences 

**Why not keep (almost) everything free?** 

* Brings many new readers, but
* High WTP readers have less reason to subscribe

---
class: font160
# Paywall Design Choices 

How to best design a paywall? 

* **Quantity choice**: how many free articles per time period? 
* **Breadth**: How much content (topics) can unsubscribed view?
* **Temporal Differentiation:** Full access on specified days? Special Issues? 
* **Porosity**: Should referrals from search engines, social media etc be exempt? 

---
class: font160
# This paper

**Strategic question**: How does changes in paywall design impact content demand and subscriptions?

* Design choices at play: quantity and breadth

**Why this matters?**

* Want to design effective paywalls 
* That balance the costs and benefits

---
class: font140
# The Experiment

**Application**: NYT paywall change in 2013 

**Before**: 

* 10 articles per month via website if unsubscribed
  * Extra articles if referred 
* Unlimited from mobile app in "top news" and "video" sections

**After**: 

* Metering mobile app ...
* 3 articles per day from any section if unsubscribed 

**Control Group**: Subscribed Readers

**Treatment Group**: Unsubscribed Readers

Natural Experiment $\implies$ **Diff-in-Diff**

<!---
# Paywall Design Space 

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/paywall_design_space.png"
knitr::include_graphics(url)
```
---> 

---
# (Natural )Experiment

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/paywall_experiment.png"
knitr::include_graphics(url)
```

---
class: font160
# Consumption 

```{r, echo = FALSE, fig.align = "center", out.width="80%"}
url <- "figs/paywall_readership.png"
knitr::include_graphics(url)
```

* Consumption declines 
* Spills over to unaffected browser views
* Greatest effect on registered but not subscribed 
  * See table 3 in paper


---
class: font140
# Subscriptions 

```{r, echo = FALSE, fig.align = "center", out.width="100%"}
url <- "figs/paywall_subscriptions.png"
knitr::include_graphics(url)
```

Split consumers into two "types": 

* **Exceed Quantity**: exceeded quota, no interest in previously blocked sections 
* **More Diverse**: not exceed quota, accessed blocked sections

---
class: font140
# Takeaways

* **More paywalled content decreases content demand**, with **modest increase in subscriptions** 
  * Open question: Where did the readers substitute towards? 
* Back of the envelope calculations suggest this increased revenue
  * Subscription gain > advertisment loss
* Suggestive that online content providers should consider a switch away from ad revenue based models 
  * But I think we need more evidence than this 
* What's missing in this work? (for me)
  * Changing two things at once makes it hard to pin down the mechanisms at play 
  * But the authors weren't in control of the experiment ... 

